Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-27 Paper/MSRChallenge2017.tex
a bit of tightening; will wait on bibtex and stats changes to find the last few lines

\section{Related work}
The most similar related work to this paper is a case study investigating how
social, technical, coordination, and prior-certification factors affect build
success for a project with 40 developers at IBM Toronto Labs~\cite{Hassan06}.  This work 
focused on one project and measured experience as the number of contributions to
the project while our study focuses on a wide range of open source projects and
measures experience through developers' profile information.
Another study investigated the relationship between authors, files in project,
and team organization when predicting build
success on an IBM project with 151 developers.  The study found that as the
number of authors or files in a build increases, the probability of build
success decreases~\cite{Kwan11}. A separate investigation used a dataset from the
same project and
found that team structures affected the teams' build success rate~\cite{Wolf09}.
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast with their work, we focus on the relationship between independent social 
attributes and continuous integration success.

@@

The authors gratefully acknowledge the partial support
of the AFRL under AFRL Contract No. FA8750-15-2-0075. Any views, opinions,
findings or recommendations are those of the author(s) and do not
necessarily reflect the views of the sponsoring agencies.

>>>>

\section{Related work}

The most similar related work to this paper is a case study investigating how
social, technical, coordination, and prior-certification factors affect build
success for a project with 40 developers at IBM Toronto Labs~\cite{Hassan06}.  This work 
focused on one project and measured experience as the number of contributions to
the project. We focus on a wide range of open source projects and
measure experience through developer profile information.
Another study of the relationship between authors, files in project,
and team organization and build
success on an IBM project with 151 developers found that as the
number of authors or files in a build increases, the probability of build
success decreases~\cite{Kwan11}. A separate investigation of the
same project 
found that team structure affected the teams' build success rate~\cite{Wolf09}.
Others have established relationships between both social and technical attributes and 
different measures of success, such as pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse} or evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, we look at a broader aspect of 
social factors, and focus on predicting the Travis CI build success.
Gousios et al.~\cite{gousios14} found that the commit change location is
an important indicator to commit acceptance rate, and that including
test cases increases a
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, while Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast with their work, we focus on the relationship between independent social 
attributes and continuous integration success.

@@

The authors gratefully acknowledge the partial support
of the AFRL (AFRL Contract No. FA8750-15-2-0075). Any 
findings or recommendations are those of the author(s) and do not
necessarily reflect the views of the sponsoring agencies.
